Decoding Toronto's Crime Patterns

### 2024-01-25 outputs/paper/paper.qmd
Update the formatting

---
title: "Decoding Toronto's Crime Patterns"
subtitle: "A Comprehensive Analysis of Victims and Trends (2014-2022)"
author: "Chay Park"
date: today
date-format: long
abstract: "In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes. Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups. The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics. This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years."
format: pdf
editor: visual
prefer-html: true
toc: true
toc-depth: 3
toc-title: Contents
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Toronto_CrimeVictims."
number-sections: true
number-depth: 3
bibliography: references.bib
---

@@

# Data

@@

The table (@tbl-totalsum-table) above illustrates the overarching trend in the number of victims across distinct age groups. The age categorization is determined by the reporting year, with the "Adult" group encompassing individuals aged 18 or older. The "Youth" group comprises individuals between the ages of 12 and 17, while those below 12 fall into the "Child" group. This presentation aims to provide a comprehensive overview of victim counts within these age cohorts over the years from 2014 to 2022.

@@

Table 1 (@tbl-totalsum-table) counts the total number of victims for each age group over the years. It is evident that the "Adult" victim group has consistently reported the highest number of incidents, while the "Child" victim group reports the least. Notably, the year 2020 stands out, revealing a substantial reduction in reported victim counts across all three age groups. This decline is attributed to the impact of COVID-19 and the ensuing lockdown measures, resulting in a significant reduction in crime reporting rates.

\newpage
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-totalsum-graph
#| fig-cap: "Number of Reported Victims of Crimes in Different Age Groups Over the Years"

@@

# Print the bar plot
print(bar_plot)
```
Graph 1 (@fig-totalsum-graph) corresponds to the information presented in table 1 (@tbl-totalsum-table). Visualizing the data by age group across each year reveals that the majority of reported crime victims fall into the "Adult" category. Notably, the bars exhibit an ascending trend from 2014 to 2018. However, a conspicuous drop in reported crimes is observed between 2019 and 2020. One plausible explanation for this decline is attributed to the impact of COVID-19, which significantly influenced crime reporting rates during this period.

From 2014 to 2020, graph 2 (@fig-sv-graph), the trend indicates that the adult group is consistently twice the size of the child group. Up until 2020, victims of sexual violation were predominantly from the adult age group. However, as of 2021, the youth victim group has surpassed the number of adult victims.

@@

@@

Graph 3 (@fig-a-graph) illustrates an ascending trend in the number of assault victims in the city of Toronto from 2014 to 2022. COVID does not appear to be a factor influencing the trend, although the sizes of both child and youth victim groups have decreased. The youth victim group has experienced a faster growth compared to the child victim group.

@@

Graph 4 (@fig-r-graph) depicts that as of 2018, the youth group of robbery victims diminished and has remained at a lower level. The COVID pandemic is a significant factor influencing the bar graphs depicting the number of robbery victims in different age groups over the years. In 2020, victims of robbery in every age group significantly decreased, indicating a possible impact of lockdown mandates on the decrease in victims.

@@

>>>>

---
title: "Decoding Toronto's Crime Patterns"
subtitle: "A Comprehensive Analysis of Victims and Trends (2014-2022)"
author: "Chay Park"
date: today
date-format: long
abstract: "In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes. Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups. The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics. This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years."
format: pdf
prefer-html: true
toc: true
toc-depth: 3
toc-title: Contents
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Toronto_CrimeVictims."
number-sections: true
number-depth: 3
bibliography: references.bib
---

@@

# Data {#sec-data}

@@

## Results

### Number of Victims by Age Group

@tbl-totalsum-table above illustrates the overarching trend in the number of victims across distinct age groups. The age categorization is determined by the reporting year, with the "Adult" group encompassing individuals aged 18 or older. The "Youth" group comprises individuals between the ages of 12 and 17, while those below 12 fall into the "Child" group. This presentation aims to provide a comprehensive overview of victim counts within these age cohorts over the years from 2014 to 2022.

@@

@tbl-totalsum-table counts the total number of victims for each age group over the years. It is evident that the "Adult" victim group has consistently reported the highest number of incidents, while the "Child" victim group reports the least. Notably, the year 2020 stands out, revealing a substantial reduction in reported victim counts across all three age groups. This decline is attributed to the impact of COVID-19 and the ensuing lockdown measures, resulting in a significant reduction in crime reporting rates.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-totalsum-graph
#| fig-cap: "Number of Reported Victims of Crimes in Different Age Groups Over the Years"

@@

@fig-totalsum-graph corresponds to the information presented in @tbl-totalsum-table. Visualizing the data by age group across each year reveals that the majority of reported crime victims fall into the "Adult" category. Notably, the bars exhibit an ascending trend from 2014 to 2018. However, a conspicuous drop in reported crimes is observed between 2019 and 2020. One plausible explanation for this decline is attributed to the impact of COVID-19, which significantly influenced crime reporting rates during this period.

### Reporting Rate on Sexual Violation

From 2014 to 2020, @fig-sv-graph, the trend indicates that the adult group is consistently twice the size of the child group. Up until 2020, victims of sexual violation were predominantly from the adult age group. However, as of 2021, the youth victim group has surpassed the number of adult victims.

@@

### Reporting Rate on Assault

@fig-a-graph illustrates an ascending trend in the number of assault victims in the city of Toronto from 2014 to 2022. COVID does not appear to be a factor influencing the trend, although the sizes of both child and youth victim groups have decreased. The youth victim group has experienced a faster growth compared to the child victim group.

@@

### Reporting Rate on Robbery

@fig-r-graph depicts that as of 2018, the youth group of robbery victims diminished and has remained at a lower level. The COVID pandemic is a significant factor influencing the bar graphs depicting the number of robbery victims in different age groups over the years. In 2020, victims of robbery in every age group significantly decreased, indicating a possible impact of lockdown mandates on the decrease in victims.

@@

### Number of Victims for each crime

@@

# Analysis
